\section{The role of subject matter experts}

Subject matter experts, or SMEs, own the knowledge and expertise that is the
backbone of software and the foundation of digitalization. But too often this
rich expertise is not captured in a structured way and gets lost when
translating it for software developers for implementation. With the rate of
change increasing, time-to-market shortening and product variability blooming,
this indirect approach of putting knowledge into software is increasingly
untenable. It causes delays, quality problems and frustration for everybody
involved. A better approach is to empower \emph{subject matter experts} to
capture, understand, reason about data, structures, rules, behaviors and other
forms of knowledge and expertise in a precise and unambiguous form by providing
them with tailored software languages and tools that allow them to directly
edit, validate, simulate and test that knowledge. The models created this way
are then automatically transformed into program code. The \emph{software
engineers} focus their activities on building these languages, tools and
transformations, plus robust execution platforms for the generated code.

\todo{Refer to Manifesto}

\section{(Where) Does this work?}

\todo{Refer to Existing publications on DSL stuff to show this works}

\todo{Discuss my domain-suitability thing}


\section{Can SMEs do that?}




\section{Difference between programming and SME'ing}


\section{Where and how to learn}

Comp think
Felienne
Mein Prog Basics stuff


